---
title: "R Markdown Live"
author: "Aijing Zhang"
date: "July 17, 2017"
output: 
    html_document
      #toc:true
      #toc_float:true
      #code_folding:hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE)
```

## Load babynames
I'm first going to load the "babynames" package. 

```{r load_babynames}
library(babynames)
library(dplyr)
library(ggplot2)
```

These data have `r nrow(babynames)` rows.
Here's the first rows of baby names: 

```{r head_babynames}
head(babynames)
```

## Grab the Karls
I want to pull out the rows with "Karl" or "Carl".
```{r grab_ckarl_rows}
karl <- babynames %>%
    filter(name=="Karl" | name=="Carl")
```


The Carl/Karl subset has `r nrow(karl)` rows.

Here's an interactive table, using the package DT:
```{r DT_karl}
library(DT)
datatable(karl)
```


## Make some plots
Here's a plot of those names over time. 

```{r plot_karl, fig.height=8}
ggplot(karl, aes(x=year, y=prop, color=name, linetype=sex)) +
    geom_line()
```


Here's an interactive version using the package plotly.
```{r plotly_karl}
library(plotly)
p <- ggplot(karl, aes(x=year, y=prop, color=name, linetype=sex)) + 
   geom_line()
   plotly::ggplotly(p)
```
