---
title: "vitD"
author: "Aijing Zhang"
date: "July 17, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE)
```

## Load the data
First load the data

1. a dataset relating physiologic response to serum level (priemelDataReconstruction.csv).
2. a dataset summarizing results from several clinical trials relating dietary intake levels in IU to serum levels in nmol/L, mostly transcribed from Table 5-4 in the IOM report (iomReview.csv). Careful with this one; it was assembled for human readability, and has blank lines.
3. metadata for the dose response dataset (vitD.R).

```{r load_data}
mydata <- read.csv(file="priemelDataReconstruction.csv", header=TRUE, sep=",")
mydata2 <- read.csv(file="iomReview.csv", header=TRUE, sep=",")
library(dplyr)
library(ggplot2)
```

Reconstructed data have `r nrow(mydata)` rows.   Review data have `r nrow(mydata2)` rows.
Here's the first rows of datat: 

```{r head_mydata}
head(mydata)
head(mydata2)
```

## Plot the data
Plot the physiologic response (OV/BV) as a function of serum level.
```{r plot_mydata}
ggplot(mydata, aes(x=SerumLevelInNgPerMl, y=OV.BV)) +
    geom_line()
```


Describe the trend.

## Fit the data
Using logistic regression to fit the probability that requirements are met (OV/BV is 2 or less) as a function of serum level. 
```{r logfit_mydata}
model <- glm(OV.BV<=2 ~.,family=binomial(link='logit'),data=mydata)
summary(model)
```

Restrict the set of patients to exclude those with serum values far from the target level (e.g., 10 nmol/L or less)
```{r logfit_mydatasub}
mydatasub <- subset(mydata,SerumLevelInNgPerMl<=10)
```



Which estimate would you trust more?

Describe the fit in text. 

State what the coefficient values are inline, rounded to 3 decimal places.

## Decribe the trend
Invoke the earlier plot chunk to set things up, and then superimpose the regression fit. Use abline to add a horizontal line at your estimate of the serum level at which 97.5% of the people would have their requirements met.




